---
title: | 
  Are repeatedly extorted businesses different? A multilevel hurdle model of extortion
  victimization: RnR analyses
author: 
  - "Patricio R. Estévez Soto"
  - "Shane D. Johnson"
  - "Nick Tilley"
email: "patricio.estevez@ucl.ac.uk"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

# Introdution

Script to conduct analyses required to resubmit a revised version of manuscript.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      dev=c("png", "CairoPDF"),
                      error=TRUE,
                      fig.width=6, fig.height=5)
options(knitr.kable.NA = '--')
```

# Set up

To ensure reproducibility and aid in debugging, we first start setting up options and printing the information about the R session.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)

```



Next we load the packages that will be used in the analysis. The installation of these packages should have already been done before. Additionally, we'll import some functions that are required, without importing the entire packages.

```{r packages}
library(victim)
library(tidyverse)
library(downloader)
library(lmtest)
library(magrittr)
#library(glmmTMB)
library(lazyeval)
library(glmmADMB)
#library(texreg)
# library(arsenal)
# library(bbmle)
# library(gridExtra)
library(parallel)
library(ggthemes)

# install.packages("pbapply")
library(pbapply)

# library(boot)


read.dbf <- foreign::read.dbf
kable <- knitr::kable
melt <- reshape2::melt
select <- dplyr::select
Anova <- car::Anova
ks.test <- dgof::ks.test



sessionInfo()

# Create csv dir for model results
dir.create("coef_results")

```


Next we load some custom functions. Ideally these should be in a separate stand-alone package, but I have not had the time to create such package.

```{r functions}

mylog <- function(x, center = FALSE){
    if(min(x) <= 0) {tlog <- log1p}
    else {tlog <- log}

    logx <- tlog(x)

    if(isTRUE(center))
    {
        logx <- logx - tlog(mean(x))
    }

    if(is.numeric(center)){
        logx <- logx - tlog(center)
    }

    return(logx)

}

mkbin <- function(x,n = 0) ifelse(x > n, 1, 0)

capadjust <- function(x, y, K = 0) x/(K-y)

# Unconditional truncated means

tnb_mean <- function(mu, alpha) mu/(1-(1+alpha*mu)^(-1/alpha))
tp_mean <- function(mu) mu/(1-exp(-mu))


countsummary <- function(model){
    print(summary(model))
    print(confint(model))
    sgm <- sigma(model)

    if(length(sgm) == 0){
        sgm <- model$alpha
    }
    cat("\n\nAlpha: \n")
    print(1/sgm)
    cat("\nLog-likelihood: \n")
    print(logLik(model))
    cat("\n")
    print(car::Anova(model))
    print(lrtest(model))
    print(car::vif(model))
}

compare_nested <- function(...) {
    print(AICtab(...))
    print(lrtest(...))
}


### Function to extract model coefficients to csv
## Should work for glmmTMB and glmmADMB models

coef_csv <- function(model, dir = "coef_results/"){
    if(class(model) == "glmmTMB"){
        coefs1 <- fixef(model)$cond
        ses1 <- sqrt(diag(vcov(model)$cond))
    } else{
        coefs1 <- coef(model)
        ses1 <- sqrt(diag(vcov(model)))
    }
    ncoefs1 <- length(coefs1)
    ses1 <- ses1[1:ncoefs1]

    confints1 <- confint(model)

    confints1 <- confints1[1:ncoefs1,1:2]

    mat <- cbind(coefs1,ses1,confints1)
    colnames(mat) <- c("Estimate", "SE", "CI_low", "CI_high")

    mname <- deparse(substitute(model))

    filename <- paste0(dir, mname, ".csv")

    write.csv(mat, file = filename)

    message("\nFile: '", filename, "' successfully writen!\n")

}

```


# Data input and processing

We first load and arrange the area and victim level data.

As the script is designed to be run remotely, when working locally during development, testing data needs to be downloaded from github. To download the testing data, the script uses an Rmarkdown parameter (`params$test`). The parameter is set to `FALSE` by default, so that it runs seamlessly using the `render` command when running in the remote research settings. For running correctly in a testing setting, the parameter must be given a `TRUE` value when running the knit command (`rmarkdown::render('ENVE_rv_ext_type.Rmd', params = list(test = TRUE))`). When using `knitr`, no parameter is passed, so the following gives an error. This is expected behaviour.

```{r testing}
#params <- list(test = TRUE)
if(params$test){
    download("https://raw.githubusercontent.com/prestevez/datahouse/master/enve2014cuest_ciega_2014.dbf",
                      destfile = "enve2014cuest_ciega_2014.dbf", mode = "wb")
}

```

Next we explore what files are available in the working directory.

```{r files}

list.files()

```

Next we input the additional data needed for the analysis currently saved in Github.

```{r GH-data}

cat_entidades <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/cat_entidades.csv", head=TRUE)
state_level_data <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/state_level_data_2013.csv", header=TRUE)
state_level_data <- merge(state_level_data,
                          cat_entidades, by="CVE_ENT", all.x=TRUE)
scode <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/secode.csv", head=TRUE)
scode$Code <- scode$Code*10000


```

Calculate the national means of the state-level variables used in the models.

```{r state-level-means}

mean_bribes <- mean(state_level_data$bribes_abvic)
mean_bribes

mean_armas <- mean(state_level_data$armas)
mean_armas

mean_drogas <- mean(state_level_data$drogas)
mean_drogas

mean_poblacion <- mean(state_level_data$poblacion)
mean_poblacion

mean_N <- mean(state_level_data$N)
mean_N

mean_General <- mean(state_level_data$General)
mean_General

mean_Derecho <- mean(state_level_data$Derecho)
mean_Derecho


```

Now we are ready to input the victim-level data.

```{r victim-level-import}
enve_all <- read.dbf("enve2014cuest_ciega_2014.dbf")

```

To prepare the data for analysis we select only the variables that are used in the analysis.

```{r victim-level-processing}

enve_test <- data.frame(extortions=as.integer(as.character(enve_all$P26_10)))

enve_test$extortion_victim <- enve_all$P25_10
enve_test$extortions[enve_test$extortion_victim == 2] <- 0
summary(enve_test$extortions)
table(enve_test$extortions)

enve_test$extortions[is.na(enve_test$extortions)] <- 0

summary(enve_test$extortions)
table(enve_test$extortions)


enve_test$rep_extortion_victim <- mkbin(enve_test$extortions, 1)
#enve_test$rep_extortion_victim <- factor(enve_test$extortions)
#levels(enve_test$rep_extortion_victim) <- c(0, 0,
#                    rep(1, length(levels(enve_test$rep_extortion_victim)) - 2))

table(enve_test$rep_extortion_victim)

enve_test$rep_extortions <- enve_test$extortions
enve_test$rep_extortions[enve_test$rep_extortions > 0] <- enve_test$rep_extortions[enve_test$rep_extortions > 0] - 1

summary(enve_test$rep_extortions)
table(enve_test$rep_extortions)


enve_test$CVE_UNICA <- as.integer(as.character(enve_all$ID_CONSECU))

enve_test$bribes <- as.integer(as.character(enve_all$P33))
summary(enve_test$bribes)

# 4 bribe cats
enve_test$bribe1 <- enve_all$P29_1
enve_test$bribe2 <- enve_all$P30_1
enve_test$bribe3 <- enve_all$P31_1
enve_test$bribe4 <- enve_all$P32_1

enve_test$bribes[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

summary(enve_test$bribes)

enve_test$bribes[is.na(enve_test$bribes)] <- 0

enve_test$bribe_victim <- mkbin(enve_test$bribes, 0)

table(enve_test$bribe_victim)

enve_test$rep_bribe <- mkbin(enve_test$bribes, 1)

table(enve_test$rep_bribe)

enve_test$bribe_cats <- factor(enve_test$bribes)
levels(enve_test$bribe_cats) <- c(0, 1, 2, rep("3+",
                                            length(levels(enve_test$bribe_cats)) - 3))
summary(enve_test$bribe_cats)

enve_test$CVE_ENT <- as.integer(as.character(enve_all$CVE_ENT))

enve_test$size <- enve_all$ID_ESTRATO
levels(enve_test$size) <- c("Large", "Medium", "Small", "Micro")

enve_test$sector <- enve_all$SECTOR_FIN

# subsector
enve_test$tempsub <- as.integer(as.character(enve_all$P1_1B))
enve_test$subsector <- cut(enve_test$tempsub, scode$Code, right=FALSE)
levels(enve_test$subsector) <- scode$Sector
enve_test$subsector <- droplevels(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)

enve_test$subsector_safe <- enve_test$subsector

# Merge utilities and construction in "other industry" category

enve_test$subsector %>%
  fct_collapse("Other industry" = c("Mining", "Construction")) %>%
  fct_relevel("Other industry", after = 3) -> enve_test$subsector

levels(enve_test$subsector)[17] <- "Other services"

levels(enve_test$subsector)

enve_test$years <- 2013 - as.numeric(as.character(enve_all$P3))
summary(enve_test$years)

intyears <- classInt::classIntervals(enve_test$years, 5, style="quantile")
enve_test$yearsquant <- cut(enve_test$years, intyears$brks, right=TRUE,
                            include.lowest = TRUE)

enve_test <- merge(enve_test, state_level_data, by="CVE_ENT", all.x=TRUE)

length(enve_test$extortions[is.na(enve_test$extortions)])
length(enve_test$bribes[is.na(enve_test$bribes)])

## enve_test$extortions[is.na(enve_test$extortions)] <- 0
## enve_test$bribes[is.na(enve_test$bribes)] <- 0

summary(enve_test)

# Exclude Corporate and Utilitites

nrow(enve_test) # should be 28179

enve_test %>%
    filter(!subsector %in% c("Utilities", "Corporate")) -> enve_test_2

enve_test_2$subsector <- droplevels(enve_test_2$subsector)

levels(enve_test_2$subsector)

enve_test_2$subsector_safe <- droplevels(enve_test_2$subsector_safe)
levels(enve_test_2$subsector_safe)

nrow(enve_test_2) # should be 28161

enve_test <- enve_test_2
nrow(enve_test)

summary(enve_test)
```


# EDA

Re-do some of the EDA

## Univariate extortion analysis

Distribution, lorenz plots and poisson tests for the aggregated extortion counts in the screening questionnaire

```{r univariate-EDA}

(extortion_dist <- victim_table(enve_test$extortions))

victim_table(enve_test$extortions, print_option = "pandoc")

(ext_cummulative <- victim_cumulative(extortion_dist))

kable(ext_cummulative, format = "pandoc", digits = 3)

```

```{r extortions1-lorenz}

victim_lorenz("extortions", data = enve_test, family = "poisson")

```

Now do some MC gini tests, Index of dispersion tests, and KS tests

```{r extortions1-tests}

mc_gini_test("extortions", enve_test, family = "poisson", plots = TRUE)

my_ks_test("extortions", enve_test)


MASS::fitdistr(enve_test$extortions, "Negative Binomial")

```

# Models

Reproduce the models presented in the submitted manuscript. (use subsector_safe)

- Null vs Full
- MNB (MTNB) vs MPoisson (MTP)
- 

Calculate VIFs.

Post-hoc robustness checks:
- Checking for outliers
  - Option one, cap extortions at 10
  - Option two, exclude incidents that suffered more than 10 extortions
  - Option three, bootstrap (100 reps?)
  - Option four, try MCMC??? (post-hoc check on admb objects, or try MCMCglmm package)


To avoid any problems with NA values that may lead to non-convergence, work with a data set onf only the relevant variables.

```{r model-data-frame}

enve_test %>%
    dplyr::select(extortions,
           bribes,
           yearsquant,
           subsector = subsector_safe,
           size,
           bribes_abvic,
           drogas,
           armas,
           Derecho,
           General,
           poblacion,
           N,
           state = NOM_ABR) -> enve_model

#### JUST FOR THIS TESTING EXERCISE, ADD MORE VICTIMS TO THE OTHER, MEDIA, and mining categories

##### Comment out before sending #####

enve_model$extortions[which(enve_model$subsector == "Other")] <- rpois(10,1)


enve_model$extortions[which(enve_model$subsector == "Media")] <- rpois(45, 0.5)

enve_model$extortions[which(enve_model$subsector == "Mining")] <- rpois(30, 1)
##### Comment out before sending #####

##### Return to normal


summary(enve_model)

length(enve_model[is.na(enve_model)])


```

Perhaps best not to use the failsafe function. Use previous results from revision 2017 to judge feasibility of glmmadmb


```{r model-failsafe-functions}

# model_failsafe <- function(formula, data, family, ndi = 60000, ...)
# {
#     model <- tryCatch(glmmADMB::glmmadmb(formula = formula,
#                                 data = data,
#                                 family = family,
#                                 zeroInflation = FALSE, 
#                                 ...,
#                                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
#                                 extra.args = paste0("-ndi", ndi)), 
#                       error = function(e)
#                           {
#                           print("glmmADMB failed")
#                           print(e)
#                           e
#                           })
#     
#     #tc <- tryCatch(summary(model), error = function(e) e)
#     
#     if(is(model, "error"))
#     {
#         print("glmmADMB failed, trying fit with glmmTMB")
#       
#        if(family == "nbinom")
#           {
#             family <- "nbinom2"
#           }
#        if(family == "truncnbinom")
#           {
#             family <- "truncated_nbinom2"
#           }
#           
#       model <- tryCatch(glmmTMB(formula = formula,
#                                 data = data,
#                                 family = family),
#                           error = function(e) e)
#         if(is(model, "error"))
#         {
#             print(model)
#             print("Second attempt also failed")
#         }
#     }
#     else {print("The model was fitted correctly with glmmadmb")}
#     
#     return(model)
# }

```


```{r main-formula}

count_formula <- extortions ~
                            bribes +
                            yearsquant +
                            subsector +
                            size +
                            mylog(bribes_abvic, mean_bribes) +
                            mylog(armas, mean_armas) +
                            mylog(drogas, mean_drogas) +
                            mylog(N, mean_N) +
                            mylog(poblacion, mean_poblacion) +
                            scale(General, mean_General, FALSE) +
                            scale(Derecho, mean_Derecho, FALSE) +
                            (1 | state)

```


```{r multilevel-negative-binomial}


mnb1 <- glmmadmb(formula = count_formula,
                 data = enve_model,
                 family = "nbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mnb1)
confint(mnb1)

coef_csv(mnb1)

get_glmmadmb(mnb1)

# vs Poisson

mp1 <- update(mnb1, family = "poisson")

summary(mp1)
confint(mp1)

get_glmmadmb(mp1)

lrtest(mp1, mnb1)

# vs single level nb

nb1 <- update(mnb1, . ~ . - (1 | state))


summary(nb1)
confint(nb1)

get_glmmadmb(nb1)

lrtest(nb1, mnb1)

vif <- car::vif

vif(mnb1)

lm1 <- lm(update(count_formula, . ~ . - (1 | state)), data = enve_model)

summary(lm1)

vif(lm1)

# NB null, multi and one level

nb_null <- update(nb1, . ~ 1)

summary(nb_null)
get_glmmadmb(nb_null)

lrtest(nb_null, nb1)

lrtest(nb_null, mnb1)

mnb_null <- update(nb_null, . ~ (1 | state))

summary(mnb_null)
get_glmmadmb(mnb_null)

lrtest(nb_null, mnb_null)

lrtest(mnb_null, mnb1)


```

The above should be equal to the MNB results reported in the manuscript.

Now, do post-hoc robustness checks:
- Checking for outliers
  - Option one, cap extortions at 10
  - Option two, exclude incidents that suffered more than 10 extortions
  - Option three, bootstrap (500 reps)
  - Option four, try MCMC??? (post-hoc check on admb objects, or try MCMCglmm package)




```{r bootstrap-function}

# use parLapply instead of mclapply

boot_model <- function(model, reps, data, cores = detectCores()){
  # set cores for parallel processing
  if(.Platform$OS.type == "windows") {
  cores <- makeCluster(cores)
  }
  
  # Export required objects to parLapply
  if(!is.integer(cores)){
    message("cores not an integer")
    
    # Export model to cluster
    mname <- deparse(substitute(model))
    clusterExport(cores, list(mname, 
                              "mylog", 
                              "mkbin",
                              "mean_bribes",
                              "mean_armas",
                              "mean_drogas",
                              "mean_poblacion",
                              "mean_N",
                              "mean_General",
                              "mean_Derecho"))
    
    # Load glmmADMB in cluster
    clusterEvalQ(cores, library(glmmADMB))
    clusterSetRNGStream(cores, iseed = 42)
  }
  
  
  # generate data replicates
  n <- nrow(data)
  data_boot <- replicate(reps, data[sample(1:n, n, replace = TRUE),], simplify = FALSE)

  models <- pblapply(data_boot, function(x){
    tryCatch(
      update(model, data = x),
      error = function(e) NULL
      )
  }, cl = cores)
  
  rslts <- list(observed = model, estimated_boot = models)
  
  # Stop cluster
  if(!is.integer(cores)){
    message("stopping cluster")
    stopCluster(cores)  
  }
  
  class(rslts) <- c("myboot", class(rslts))
  return(rslts)
}

# Write helper functions to extract myboot objects
coef.myboot <- function(myboot_obj){
  obj <- myboot_obj$estimated_boot
  obj <- obj[!sapply(obj, is.null)]
  obj_coefs <- sapply(obj, function(x) coef(x))
  # obj_coefs <- lapply(obj, function(x) coef(x))
  # obj_coefs <- unnest(obj_coefs)
  # print(obj_coefs)
  
  # add alpha
  alphas <- sapply(obj, function(x){
    a <- 1/x$alpha
    if(length(a) == 0){
      a <- NA
    }
    a
    })
  if(!all(is.na(alphas))){
    obj_coefs <- rbind(obj_coefs, "alpha" = alphas)
  }
  
  # Var_j
  if(!is.null(myboot_obj$observed$random)){
    vars_j <- sapply(obj, function(x) as.numeric(x$S))
    obj_coefs <- rbind(obj_coefs, "var_j" = vars_j)
  }
  
  return(obj_coefs)
}

obs_boot <- function(myboot_obj){
  if(!"myboot" %in% class(myboot_obj)){
    stop("This is not a myboot object")
  }
  
  obs <- myboot_obj$observed
  coefs <- coef(obs)
  
  alpha <- 1/obs$alpha
  if(length(alpha) != 0){
    coefs <- c(coefs, "alpha" = alpha)
  }

  if(!is.null(obs$random)){
    var_j <- as.numeric(obs$S)
    names(var_j) <- "var_j"
    coefs <- c(coefs, var_j)
  }
  
  coefs_mat <- matrix(coefs)
  row.names(coefs_mat) <- names(coefs)

  return(coefs_mat)
}


confint.myboot <- function(myboot_obj,
                           sig = 0.95,
                           type = c("perc", "bc")){
  
  # extract coefs
  coefs <- coef(myboot_obj)
  
  # alpha level
  a <- (1-sig)/2
  a <- c(a, 1-a)
  
  # Observed values
  obs <- obs_boot(myboot_obj)
  
  # Replicates
  R <- ncol(coefs)
  
  # Terms
  terms <- nrow(coefs)
  
  # Percent
  if(type[1] == "perc"){
    p <- a
    ci <- apply(coefs, 1, quantile, probs = p)
    ci <- t(ci)
  }
  
  # bias-corrected
  if(type[1] == "bc"){
    b <- sapply(1:terms, function(x) qnorm(sum(coefs[x,] < obs[x,])/R))
    z <- qnorm(a)
    p_l <- pnorm(z[1]-2*b)
    p_h <- pnorm(z[2]-2*b)
    pm <- cbind(p_l, p_h)
    ci <-sapply(1:terms, function(x) quantile(coefs[x,], probs = pm[x,]))
    rownames(ci) <- c("BC 2.5%", "BC 97.5%")
    colnames(ci) <- rownames(coefs)
    
    # Bias corrected estimate
    boot_mean <- sapply(1:terms, function(x) mean(coefs[x,]))
    bcm <- cbind(2*obs - boot_mean)
    colnames(bcm) <- "BC Estimate"
    ci <- cbind(bcm, t(ci))
  }
  
  # return ci
  return(ci)
}

summary.myboot <- function(myboot_obj, sig = 0.95){
  obs <- obs_boot(myboot_obj)
  coefs <- coef(myboot_obj)
  se_boot <- apply(coefs, 1, sd, na.rm = TRUE)
  ci_perc <- confint(myboot_obj, sig)
  ci_bc <- confint(myboot_obj, sig, type = "bc")
  message(paste0("Valid bootstrap replicates: ", ncol(coefs)))
  z <- obs/se_boot
  p <-  pnorm(-abs(z))
  rslts <- cbind(Estimate = obs, SE = se_boot,  z, p, ci_perc, ci_bc)
  colnames(rslts)[c(1, 3:4)] <- c("Estimate", "Z-score", "p-value")
  return(rslts)
}



# Plot method to generate a ridge forest plot
# 
# Save coef.myboot object to facilitate plotting of BS distributions

# save csv method for summary.myboot

coef_csv_boot <- function(myboot_obj, dir = "coef_results/"){
    if("myboot" %in% class(myboot_obj)){
      mat <- summary(myboot_obj)
    } else{
      stop("This is not a myboot object")
    }
  
    mname <- deparse(substitute(myboot_obj))

    filename <- paste0(dir, mname, ".csv")

    write.csv(mat, file = filename)

    message("\nFile: '", filename, "' successfully writen!\n")

}


```


Calculate bootstrap SE and CIs for mnb1

```{r boot-mnb1}

boot_r <- 5

mnb1_boot <- boot_model(mnb1, boot_r, enve_model)

summary(mnb1_boot)

coef_csv_boot(mnb1_boot)

write.csv(coef(mnb1_boot), file = "coef_results/mnb1_boot_reps.csv")

```


## Logit model



```{r multilevel-logit}


mlogit1 <- update(mnb1, mkbin(extortions) ~ ., 
                  family = "binomial")

summary(mlogit1)
confint(mlogit1)

coef_csv(mlogit1)

get_glmmadmb(mlogit1)

# vs single level logit

logit1 <- update(mlogit1, . ~ . - (1 | state))


summary(logit1)
confint(logit1)

get_glmmadmb(logit1)

lrtest(logit1, mlogit1)

# logit null, multi and one level

logit_null <- update(logit1, . ~ 1)

summary(logit_null)
get_glmmadmb(logit_null)

lrtest(logit_null, logit1)

lrtest(logit_null, mlogit1)

mlogit_null <- update(logit_null, . ~ (1 | state))

summary(mlogit_null)
get_glmmadmb(mlogit_null)

lrtest(logit_null, mlogit_null)

lrtest(mlogit_null, mlogit1)


```

Bootstrap mlogit1


```{r boot-mlogit}

mlogit1_boot <- boot_model(mlogit1, boot_r, enve_model)

summary(mlogit1_boot)

coef_csv_boot(mlogit1_boot)

write.csv(coef(mlogit1_boot), file = "coef_results/mlogit1_boot_reps.csv")

```

# Truncated models



```{r multilevel-truncated-model}

# Truncated data

enve_model %>%
  filter(extortions > 0) -> t_enve_model

mtnb1 <- glmmadmb(formula = count_formula,
                 data = t_enve_model,
                 family = "truncnbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mtnb1)
confint(mtnb1)

coef_csv(mtnb1)

get_glmmadmb(mtnb1)

# vs Poisson

mtp1 <- update(mtnb1, family = "truncpoiss")

summary(mtp1)
confint(mtp1)

get_glmmadmb(mtp1)

lrtest(mtp1, mtnb1)

# vs single level nb

tnb1 <- update(mtnb1, . ~ . - (1 | state))


summary(tnb1)
confint(tnb1)

get_glmmadmb(tnb1)

lrtest(tnb1, mtnb1)

vif(mtnb1)

tlm1 <- lm(update(count_formula, . ~ . - (1 | state)), data = t_enve_model)

summary(tlm1)

vif(tlm1)

# NB null, multi and one level

tnb_null <- update(tnb1, . ~ 1)

summary(tnb_null)
get_glmmadmb(tnb_null)

lrtest(tnb_null, tnb1)

lrtest(tnb_null, mtnb1)

mtnb_null <- update(tnb_null, . ~ (1 | state))

summary(mtnb_null)
get_glmmadmb(mtnb_null)

lrtest(tnb_null, mtnb_null)

lrtest(mtnb_null, mtnb1)


```

Calculate bootstrap SE and CIs for mtnb1

```{r boot-mtnb1}

mtnb1_boot <- boot_model(mtnb1, boot_r, t_enve_model)

coef(mtnb1_boot)

summary(mtnb1_boot)

coef_csv_boot(mtnb1_boot)

write.csv(coef(mtnb1_boot), file = "coef_results/mtnb1_boot_reps.csv")

```


# Outlier check

Check which are the observations with outliers, what are their characteristics.

Drop outliers as a sanity check.
  - Exclude observations that suffered 30 or more extortions
  - Cap observations that are greater than 10 at 10 (ugh)
  
Dropping "outliers" first.
  
```{r drop-less-than-30}

enve_model %>%
  filter(extortions < 30) -> enve_drop


mnb1_drop <- glmmadmb(formula = count_formula,
                 data = enve_drop,
                 family = "nbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mnb1_drop)
confint(mnb1_drop)

coef_csv(mnb1_drop)

get_glmmadmb(mnb1_drop)

vif(mnb1_drop)

# vs Poisson

mp1_drop <- update(mnb1_drop, family = "poisson")

summary(mp1_drop)
confint(mp1_drop)

get_glmmadmb(mp1_drop)

lrtest(mp1_drop, mnb1_drop)

# vs single level nb

nb1_drop <- update(mnb1_drop, . ~ . - (1 | state))


summary(nb1_drop)
confint(nb1_drop)

get_glmmadmb(nb1_drop)

lrtest(nb1_drop, mnb1_drop)

# NB null, multi and one level

nb_null_drop <- update(nb1_drop, . ~ 1)

summary(nb_null_drop)
get_glmmadmb(nb_null_drop)

lrtest(nb_null_drop, nb1_drop)

lrtest(nb_null_drop, mnb1_drop)

mnb_null_drop <- update(nb_null_drop, . ~ (1 | state))

summary(mnb_null_drop)
get_glmmadmb(mnb_null_drop)

lrtest(nb_null_drop, mnb_null_drop)

lrtest(mnb_null_drop, mnb1_drop)

## Logit

mlogit1_drop <- update(mnb1_drop, mkbin(extortions) ~ ., 
                  family = "binomial")

summary(mlogit1_drop)
confint(mlogit1_drop)

coef_csv(mlogit1_drop)

get_glmmadmb(mlogit1_drop)

# vs single level logit

logit1_drop <- update(mlogit1_drop, . ~ . - (1 | state))


summary(logit1_drop)
confint(logit1_drop)

get_glmmadmb(logit1_drop)

lrtest(logit1_drop, mlogit1_drop)

# logit null, multi and one level

logit_null_drop <- update(logit1_drop, . ~ 1)

summary(logit_null_drop)
get_glmmadmb(logit_null_drop)

lrtest(logit_null_drop, logit1_drop)

lrtest(logit_null_drop, mlogit1_drop)

mlogit_null_drop <- update(logit_null_drop, . ~ (1 | state))

summary(mlogit_null_drop)
get_glmmadmb(mlogit_null_drop)

lrtest(logit_null_drop, mlogit_null_drop)

lrtest(mlogit_null_drop, mlogit1_drop)


# Truncated data

mtnb1_drop <- glmmadmb(formula = count_formula,
                 data = filter(enve_drop, extortions > 0),
                 family = "truncnbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mtnb1_drop)
confint(mtnb1_drop)

coef_csv(mtnb1_drop)

get_glmmadmb(mtnb1_drop)

# vs Poisson

mtp1_drop <- update(mtnb1_drop, family = "truncpoiss")

summary(mtp1_drop)
confint(mtp1_drop)

get_glmmadmb(mtp1_drop)

lrtest(mtp1_drop, mtnb1_drop)

# vs single level nb

tnb1_drop <- update(mtnb1_drop, . ~ . - (1 | state))


summary(tnb1_drop)
confint(tnb1_drop)

get_glmmadmb(tnb1_drop)

lrtest(tnb1_drop, mtnb1_drop)

vif(mtnb1_drop)

# NB null, multi and one level

tnb_null_drop <- update(tnb1_drop, . ~ 1)

summary(tnb_null_drop)
get_glmmadmb(tnb_null_drop)

lrtest(tnb_null_drop, tnb1_drop)

lrtest(tnb_null_drop, mtnb1_drop)

mtnb_null_drop <- update(tnb_null_drop, . ~ (1 | state))

summary(mtnb_null_drop)
get_glmmadmb(mtnb_null_drop)

lrtest(tnb_null_drop, mtnb_null_drop)

lrtest(mtnb_null_drop, mtnb1_drop)


```



Capping extortions at 10


```{r capped-extortions}

enve_model %>%
  mutate(extortions = ifelse(extortions > 10, 10, extortions)) -> enve_capped

mnb1_capped <- glmmadmb(formula = count_formula,
                 data = enve_capped,
                 family = "nbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mnb1_capped)
confint(mnb1_capped)

coef_csv(mnb1_capped)

get_glmmadmb(mnb1_capped)

vif(mnb1_capped)

# vs Poisson

mp1_capped <- update(mnb1_capped, family = "poisson")

summary(mp1_capped)
confint(mp1_capped)

get_glmmadmb(mp1_capped)

lrtest(mp1_capped, mnb1_capped)

# vs single level nb

nb1_capped <- update(mnb1_capped, . ~ . - (1 | state))


summary(nb1_capped)
confint(nb1_capped)

get_glmmadmb(nb1_capped)

lrtest(nb1_capped, mnb1_capped)

# NB null, multi and one level

nb_null_capped <- update(nb1_capped, . ~ 1)

summary(nb_null_capped)
get_glmmadmb(nb_null_capped)

lrtest(nb_null_capped, nb1_capped)

lrtest(nb_null_capped, mnb1_capped)

mnb_null_capped <- update(nb_null_capped, . ~ (1 | state))

summary(mnb_null_capped)
get_glmmadmb(mnb_null_capped)

lrtest(nb_null_capped, mnb_null_capped)

lrtest(mnb_null_capped, mnb1_capped)


# Truncated data

mtnb1_capped <- glmmadmb(formula = count_formula,
                 data = filter(enve_capped, extortions > 0),
                 family = "truncnbinom", 
                 zeroInflation = FALSE,
                 admb.opts = glmmADMB::admbControl(noinit = FALSE, shess=FALSE),
                 extra.args = "-ndi 60000")

summary(mtnb1_capped)
confint(mtnb1_capped)

coef_csv(mtnb1_capped)

get_glmmadmb(mtnb1_capped)

# vs Poisson

mtp1_capped <- update(mtnb1_capped, family = "truncpoiss")

summary(mtp1_capped)
confint(mtp1_capped)

get_glmmadmb(mtp1_capped)

lrtest(mtp1_capped, mtnb1_capped)

# vs single level nb

tnb1_capped <- update(mtnb1_capped, . ~ . - (1 | state))


summary(tnb1_capped)
confint(tnb1_capped)

get_glmmadmb(tnb1_capped)

lrtest(tnb1_capped, mtnb1_capped)

vif(mtnb1_capped)

# NB null, multi and one level

tnb_null_capped <- update(tnb1_capped, . ~ 1)

summary(tnb_null_capped)
get_glmmadmb(tnb_null_capped)

lrtest(tnb_null_capped, tnb1_capped)

lrtest(tnb_null_capped, mtnb1_capped)

mtnb_null_capped <- update(tnb_null_capped, . ~ (1 | state))

summary(mtnb_null_capped)
get_glmmadmb(mtnb_null_capped)

lrtest(tnb_null_capped, mtnb_null_capped)

lrtest(mtnb_null_capped, mtnb1_capped)


```

# The end

```{r end}
date()
endtime <- proc.time()

endtime - starttime
```





























